classification

These first few functions were written for the KNN analysis. 

Gets the indices for training and testing splitting.
```{r}
getIndices <- function(percentTrain,dataset){
  actual <- percentTrain*0.01
  trSize <- as.integer(length(dataset[,1])*actual)
  cat("\n","training size is ",trSize)
  #trSize <- as.numeric(trSize)
  train <- sample.int(length(dataset[,1]),size = trSize)
  #train <- dataset[trainInd,]
  v <- c(1:20)
  test <- v[!(v %in% train)]
  #test <- dataset[testInd,]
  return(list(train,test))
}
```

Subsets training and testing sets from the initial dataset.
```{r}
setTrainAndTest <- function(percentTrain,dataset){
  indDF <- getIndices(percentTrain,dataset)
  train <- dataset[as.numeric(unlist(indDF[1])),]
  test <- dataset[as.numeric(unlist(indDF[2])),]
  return(list(train,test))
}
```

Runs KNN.
```{r}
runKNN <- function(p,set){
    cat("\n","running knn...")
    seps <- setTrainAndTest(p,set)
    tr <- as.data.frame(seps[1])
    te <- as.data.frame(seps[2])
    r <- knn(tr[,1:1000],te[,1:1000],tr$LEVEL)
    s <- compare(r,te$LEVEL)
    cat("\n",s," correct predictions","\n")
    return(s)
}
```

Compares results from KNN.
```{r}
compClassRes <- function(res,actual){
  ret <- res[actual]
  return(length(ret[ret == TRUE]))
}
```

Vector with names of classification steps. 
```{r}
classNames <- c("ibk","j48","lmt","stump",
                "ada","bag")
```

Switch function for classification types.
```{r}
classify <- function(data,type){
  res <- switch(type,
                ibk = IBk(LEVEL~.,data), 
                lbr = LBR(LEVEL~., data),
                j48 = J48(LEVEL~.,data),
                lmt = LMT(LEVEL~.,data),
                msp = M5P(LEVEL~.,data), 
                stump = DecisionStump(LEVEL~.,data),
                logi = Logistic(LEVEL~.,data),
                smo = SMO(LEVEL~.,data),
                ada = AdaBoostM1(LEVEL~.,data),
                bag = Bagging(LEVEL~.,data),
                lBoost = LogitBoost(LEVEL~.,data),
                mBoost = MultiBoostAB(LEVEL~.,data),
                stack = Stacking(LEVEL~.,data),
                cs = CostSensitiveClassifier(LEVEL~.,data))
  return(res)
}
```

Classifies all functions, takes their predictions, and compiles them into a dataset of predictions.
  'data' is the data to use for classification
  'these' is the vector with the names of the classifiers
```{r}
perform <- function(data,these){
  ini <- vector(length = 150)
  res <- data.frame(ini)
  nameVec <- vector()
  for(i in 1:length(these)){
    cat("\n",i)
    performance <- vector()
    cat("\n","Classifying with ", these[i],"...")
    performer <- classify(data,these[i])
    #celebrate()
    nameVec <- append(nameVec,these[i])
    predictions <- performer$predictions
    predictions <- as.data.frame(predictions == 1)
    if(!(i==1)){res <- cbind(res,predictions)}
       else{res <- data.frame(predictions)}
  }
  names(res) <- nameVec
  return(res)
}
```

Returns a confusion-matrix object for the classification predictions.
  'Performer' is the dataset. 
  'Performance' is the result of the perform function, the prediction dataframe
  'col' is the column containing predictions for the classifier you're testing
  'classCol' is the column containing actual classes from the original dataset
```{r}
rate <- function(performer,performance,col,classCol){
  cat("\n","What the hell is this: ",performance[,col])
  cat("\n","And this: ",performer[,classCol])
  #if(length(performance[FALSE] == 0)){return(data.matrix(1:100,"FAIL"))}
  pred <- as.factor(performance[,col])
  cat("\n",levels(pred))
  act <- as.factor(performer[,classCol])
  cat("\n",levels(act))
  if(!(length(levels(pred)) == length(levels(act)))){
    levels(pred) <- levels(act)
  }
  res <- confusionMatrix(pred,act)

  return(res)
}
```

writes all classification ratings and predictions to csv files
```{r}
writeAllPerformances <- function(){
  cat("\n","Beginning to write performances...")
  setwd(defDir)
  setwd("A")
  set <- dir()[str_detect(dir(),"EA")]
  cat("\n","Readable files are: ", set)
  for(i in 1:length(set)){
    setwd(defDir)
    setwd("A")
    cat("\n","Attempting to read ",set[i])
    thisData <- read.csv(set[i])
    thisName <- str_replace(set[i],".csv","")
    
    thisAct <- perform(thisData,classNames)
    for(j in 1:length(thisAct[1,])){
      cat("\n","Beginning judgment...")
      thisSucc <- rate(thisData,thisAct,j,length(thisData))
      setwd(defDir)
      dir.create("CM")
      setwd("CM")
      cat("\n","Writing Judgment... for ",names(thisAct)[j])
      newName <- str_c(thisName,names(thisAct)[j],".cm")
      cat("\n",newName)
      write.matrix(thisSucc,file=newName,sep=",")
      #celebrate()
    }
   # celebrate()
  }
  setwd(defDir)
  setwd("B")
  set <- dir()[str_detect(dir(),"EB")]
  for(i in 1:length(set)){
    setwd(defDir)
    setwd("B")
    thisData <- read.csv(set[i])
    thisName <- str_replace(set[i],".csv","")
    thisAct <- perform(thisData,classNames)
    for(j in 1:length(thisAct[1,])){
      thisSucc <- rate(thisData,thisAct,j,length(thisData))
      setwd(defDir)
      dir.create("CM")
      setwd("CM")
      cat("\n","Writing Judgment... for ",names(thisAct)[j])
      write.matrix(thisSucc,file=str_c(thisName,names(thisAct)[j],".cm"),sep=",")
      #celebrate()
    }
   # celebrate()
  }
}
```