Main runner for everything.
Load this script in order to run all other scripts.
Load it as source files before all others.

After this file is loaded, the user then enters two commands to begin analysis. 
init_workspace() - which loads necessary libraries and source code
runFullAnalysis(namesOfSets,type="full",subs = 0, subType=NULL) - which runs either the entire analysis or an analysis on the subsets. 
  namesOfSets is the vector with the strings with the names of the datasets the user wishes to download.
  type is the string which specifies which type of analysis the user wishes to perform. "full" performs the full analysis; "sub" performs 
  analysis on a subset of the data
  "nopp" performs an analysis without preprocessing the data.
  the subs argument specifies the length of the subset. 
  subType, when called "group", returns the group from the preprocessing function. 
  
init_workspace, when called, loads all libraries and sources.
It also initializes the directory to one the user hardcodes in...
```{r}
init_workspace <- function(){
  library(knitr)
  library(reshape2)
  library(GEOquery)
  library(refGenome)
  library(rtracklayer)
  library(limma)
  library(affy)
  library(stringr)
  library(ggplot2)
  library(caret)
  library(FactoMineR)
  library(FSelector)
  library(preprocessCore)
  library(audio)
  library(RWeka)
  source("main.R")
  source("preProcess.R")
  source("enrich.R")
  source("normalize.R")
  source("classify.R")
  defDir <- "C://Users//Brad//Desktop//rdir//"
  setwd(defDir)  
}
```

This part of the script, when run, initializes the directory automatically, 
initializes the test sound, loads the audio library, initialzes the vector of queries. 
```{r}
defDir <- "C://Users//Brad//Desktop//rdir//"
setwd(defDir)
library(audio)
death<-load.wave("LOZ_Fail.wav")
queryVector <- c("GSE4757","GSE28146", "GSE4226","GSE1297","GSE33000","GSE44768","GSE44770",
                 "GSE44771","GSE13214")
defDir <- "C://Users//Brad//Desktop//rdir//"
```

This is not used, but can be loaded for testing. 
```{r}
celebrate <- function(){
  play(celebration)
}
```

This function allows the code to refresh source code when the code has been changed.
```{r}
refreshSrcs <- function(){
  gc() #run garbage collector      
  setwd(defDir) #set default directory
  source("main.R") #load source
  init_workspace() #load other sources
}
```

This code runs the full analysis. When the source is loaded and the 
The arguments:
  namesOfSets passes the vector with the names of the GEOdatasets
  type specifies the type of analysis to be performed.
    "full" specifies that analysis should be performed on the entire query
    "sub" specifies that the analysis should be on a subset
    "nopp" performs an analysis skiping the preprocess step, analyzing all sets in the PP folder.
```{r}

runFullAnalysis <- function(namesOfSets,type="full",subs = 0, subType="groups"){
  
  setwd("C:\\Users\\Brad\\Desktop\\rdir")
  source("main.R")
  setwd(defDir)
  #bigEvent <- load.wave("LOZ_Big.wav")
  #smallEvent <- load.wave("LOZ_Small.wav")
  finished <- load.wave("LOZ_Theme.wav") #plays at the end of the program

  #play(bigEvent)
  #preprocess, downloading all datasets, converting them to csvs and writing them to files
  #switch function. Full runs full preprocessing stesp. Sub runs subsets. Nopp runs without preprocessing.
  group <- switch(type,
                  full = preProcess(namesOfSets),
                  sub = preProcessSub(namesOfSets,s = subs,ret = subType),
                  nopp = groupDataByExp(namesOfSets))
    
  #play(bigEvent)
  #reload the written csvs one-by-one (for memory preservation), and write their normalized equivalents
  loadNormalizeWrite(namesOfSets)
  
  #create the normalization directory
  dir.create("NORM")
  
  cat("\n","Beginning A compilation and enrichment...")
  
  for(i in 1:length(namesOfSets)){ #for all datasets 
    setwd("NORM")
    load <- read.csv(str_c(namesOfSets[i],"NORM.csv"),head=TRUE,sep=",") #read the file
    #play(smallEvent)
    aEnrichWriteAllMeas(load,namesOfSets[i]) #write and enrich them all
   # play(smallEvent)
    rm(load)
    gc() #remove the garbage collector
    setwd(defDir)
  }
 # play(bigEvent)
  
  setwd(defDir)
#   
#   cat("\n","Beginning B compilation and enrichment...")
#   
#   for(j in 1:length(group[1,])){ #for all datasets
#     load <- bCompile(group[,j],row.names(group)) #load and compile the stuff from the csvs
#     #play(smallEvent)
#     bEnrichWriteAllMeas(load,names(group)[j]) #write all measures for the loaded set 
#     #play(smallEvent)
#   }
#   
 # play(bigEvent)
  setwd(defDir)
  
  cat("\n","Beginning performance...")
  writeAllPerformances() #write all classification successes
  setwd(defDir)
  play(finished)
}
```